---
title: "basic_statistics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Normal Distribution

```{r n}

m <- 3 # mean 
sd <- 2 # standard deviation
p <- 4 # prob
#dnorm(x, mean = 0, sd = 1, log = FALSE)
#pnorm(q, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
#qnorm(p, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
#rnorm(n, mean = 0, sd = 1)

## Standard normal distribution
rannorm <- rnorm(500)
par(mfrow=c(1,2)) # two plots by side
# A frequency diagram
hist(rannorm, freq=TRUE, main="")
hist(rannorm, freq=FALSE, main="", ylim=c(0,0.4))
curve(dnorm(x), add=TRUE, col="blue")

# A standard normal distribution

curve(dnorm(x, sd=1, mean=0), from=-3, to=3,
      ylab="Density", col="blue")

# Add a t-distribution with 3 degrees of freedom.

curve(dt(x, df=3), from =-3, to=3, add=TRUE, col="red")

# Add a legend (with a few options, see ?legend)

legend("topleft", c("Standard normal","t-distribution, df=3"), lty=1, col=c("blue","red"),
       bty='n', cex=0.8)
```

## Inference for a single population

Inference is answering questions about population parameters based on a sample. The mean of a random sample from a population is an estimate of the population mean. Since it is a single number it is called a point estimate. It is often desirable to estimate a range within which the population parameter lies with high probability. This is called a confidence interval.

One way to get confidence intervals in R is to use the quantile functions for the relevant distribution.

```{r inference}

alpha <- 0.05 # 95% confidence interval
xbar <- mean(rannorm)
s <- sd(rannorm)
n <- length(rannorm)
half.width <- qt(1-alpha/2, n-1)*s/sqrt(n)

# Confidence Interval
c(xbar - half.width, xbar + half.width)
```


